Khai Shen Chng
90328958
STAT251 Final Screencast

```{r}
library(dplyr)
library(stringr)
library(ggplot2)
library(purrr)
library(nlme)
library(tidyverse)
```

Reading CSV files
```{r}
team_results <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-03-26/team-results.csv')
public_picks <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-03-26/public-picks.csv')
```


Join the tables
```{r}
joint_df <- left_join(public_picks, team_results, by = "TEAM")
```


Removing any unnecessary variables/columns
```{r}
joint_df <- joint_df %>%
  select(-TEAMID, -YEAR)
```


Converting String percentages to integers
```{r}
percent_var <- c('R64.x', 'R32.x', 'S16.x', 'E8.x', 'F4.x', 'FINALS', 'F4PERCENT', 'CHAMPPERCENT')

joint_df1 <- joint_df %>%
  mutate(across(.cols = percent_var,
                .fns = ~as.numeric(str_replace(.x, "%", ""))))
```




Task 1: Which factors have higher influence on the public to pick a specific team to have a deeper championship run
```{r}
descend_df <- joint_df1 %>%
  arrange(desc(FINALS))
head(descend_df)
```
** The percentage of people picking a specific team to advance each round follows a similar pattern for all rounds


```{r}
population <- 22000000

descend_df$FINALS_pop <- descend_df$FINALS / 100 * population
```


Creating Linear Regression Model
```{r}
variables_regress <- c("PAKE", "PASE", "GAMES", "W", "WINPERCENT", "F2", "CHAMP", "TOP2")

models <- map(variables_regress, ~lm(reformulate("FINALS_pop", response = .), data = descend_df))

results_df <- map_df(models, ~{
  tibble(
    p_value_response_var = summary(.)$coefficients[2, "Pr(>|t|)"],
    r_squared = summary(.)$r.squared
  )}, 
  .id = "model_id")

results_df$variable <- variables_regress

results_df <- results_df %>%
  arrange(desc(p_value_response_var)) %>%
  mutate(r_squared = r_squared *100)

results_df
```


Visualizing Linear Regression Graphs
```{r}
map(variables_regress, ~ggplot(descend_df, aes_string(x = .x, y = "FINALS_pop")) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  labs(title = paste("Regression of target on", .x)))
```




Task 2: Is there a pattern between increasing number of loses and number of championships?
```{r}
# Assuming 'data' is your dataframe and 'column1' and 'column2' are the column names
loses_champ <- descend_df[c("TEAM", "L", "CHAMP")]

loses_champ <- loses_champ %>%
  arrange(desc(L))

head(loses_champ)
```






